Extreme heterogeneity of influenza virus infection in single cells

### 2018-02-06 paper/paper.tex
added link to cell-gene matrix provided by *eLife*
removed extra `\end{document}`
updated repository commit

\subsection{Computational analysis of single-cell mRNA sequencing data}
Jupyter notebooks that perform all of the computational analyses are available in Supplementary~file~\ref{suppfile:code} and at \url{https://github.com/jbloomlab/flu_single_cell}~\citep{russell2018github}. \jdbcomment{This GitHub repository will be made public upon acceptance of the manuscript.}

@@

\begin{suppfile}
\caption{\label{suppfile:cellgenematrix}
The annotated cell-gene matrix in Matrix Market Format.
This is the matrix generated in \texttt{./results/cellgenecounts/} by running the CellRanger analysis in \texttt{align\_and\_annotate.ipynb} in Supplementary~file~\ref{suppfile:code}.
\jdbcomment{This file is too large for the \textit{eLife} submission system, and so is in the process of being uploaded to DataDryad.}
}
\end{suppfile}

>>>>

\subsection{Computational analysis of single-cell mRNA sequencing data}
Jupyter notebooks that perform all of the computational analyses are available in Supplementary~file~\ref{suppfile:code} and at \url{https://github.com/jbloomlab/flu_single_cell}~\citep{russell2018github}.

@@

\begin{suppfile}
\caption{\label{suppfile:cellgenematrix}
The annotated cell-gene matrix in Matrix Market Format.
This is the matrix generated in \texttt{./results/cellgenecounts/} by running the CellRanger analysis in \texttt{align\_and\_annotate.ipynb} in Supplementary~file~\ref{suppfile:code}.
This file is available on DataDryad at \url{https://doi.org/10.5061/dryad.qp0t3}.
}
\end{suppfile}
